RSA_model2

### 2015-11-19 models/Model_Comparison.Rmd
initial runs for fitted and unfitted alphas for full model - need to restrict to just comparison set of scalar terms (from e6, e8)

library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)

#setwd("~/Desktop/Projects/scalar_implicature/")
#source("analysis/useful_dplyr.R")
```

@@

speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
# Uniform priors
priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
# Combine speaker / listener
data = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)

```

## Data for full model
```{r}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
```

## Run comparisons
```{r}
# Model 1 - Entailment, no alpha tuning
# -------------------------------------
m1.noFit = data %>%
  do(run.partial(., alpha = 1, useprior = T, usenone = F))
performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))

# Model 1 - Entailment, alpha tuning
# ----------------------------------
best.alpha = tune.alpha(data)
m1.fit = data %>%
  do(run.partial(., alpha = best.alpha))
performance.output[2, ] = c("M1_Fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))

# Model 2 - Entailment, generic "None", no alpha tuning
# -----------------------------------------------------
m2.noFit = data %>%
  do(run.partial(., alpha = 1, usenone = T))
performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))

# Model 2 - Entailment, generic "None", alpha tuning
# ----------------------------------
best.alpha = tune.alpha(data, usenone = T)
m2.fit = data %>%
  do(run.partial(., alpha = best.alpha, usenone = T))
performance.output[4, ] = c("M2_Fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md,
      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
                 alpha),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

>>>>

library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)
#setwd("~/Desktop/Projects/scalar_implicature/")
#source("analysis/useful_dplyr.R")
```

@@

speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
# Uniform priors
priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
# Combine speaker / listener
data.partial = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

## Data for full model
```{r}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
data.full = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

## Run comparisons
```{r}
# Model 1 - Entailment, no alpha tuning
# -------------------------------------
m1.noFit = data.partial %>%
  do(run.partial(., alpha = 1, useprior = T, usenone = F))
performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))

# Model 1 - Entailment, alpha tuning
# ----------------------------------
best.alpha = tune.alpha(data.partial)
m1.fit = data.partial %>%
  do(run.partial(., alpha = best.alpha))
performance.output[2, ] = c("M1_Fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))

# Model 2 - Entailment, generic "None", no alpha tuning
# -----------------------------------------------------
m2.noFit = data.partial %>%
  do(run.partial(., alpha = 1, usenone = T))
performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))

# Model 2 - Entailment, generic "None", alpha tuning
# ----------------------------------
best.alpha = tune.alpha(data.partial, usenone = T)
m2.fit = data.partial %>%
  do(run.partial(., alpha = best.alpha, usenone = T))
performance.output[4, ] = c("M2_Fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))

# Scalar matches between Full and partial

# Model 3 - Full, no alpha tuning
# ----------------------------------
m3.noFit = data.full %>%
  do(run.full(., alpha = 1))
performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit$listener.p, m3.noFit$pred)^2, 5))

# Model 3 - Full, alpha tuning
# ----------------------------------
best.alpha = tune.alpha(data.full, type = "full")
m3.fit = data.full %>%
  do(run.full(., alpha = best.alpha))
performance.output[6, ] = c("M3_Fit", round(cor(m3.fit$listener.p, m3.fit$pred)^2, 5))
```

Visualize
---------
```{r}
alpha = best.alpha
qplot(stars, listener.p, col=degree, 
      data=m3.fit,
      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
                 alpha),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
